Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-24 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Code corrections

source("C:/Users/U8011054/OneDrive - USQ/Cloudstor/R/Mungbean_projects/Mungbean_PM/R/import_data.R")
PM_MB_means <- import_data()

@@

Herm_17_dat <- 
   data.frame(trial_ref = "mung1617/01",
              year = "2017",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = Herm_17_dat$Plot.Length,
              plot_width = 2,
              plant_density = NA,
              row_spacing = Herm_17_dat$`Row.Spacing.(m)`,
              replicate = Herm_17_dat$Rep,
              planting_date = as.Date("2017-01-27", format = "%Y-%m-%d"),
              emergence_date = as.Date("2017-02-01", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2017-03-13", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_17_dat$trade_name),
              fungicide_ai = Herm_17_dat$fungicide_ai,
              dose_ai.ha = Herm_17_dat$dose_ai.ha,
              n_treatment = as.numeric(unlist(strsplit(Herm_17_dat$Manage.Trt, "T"))[unlist(strsplit(Herm_17_dat$Manage.Trt, "T")) != ""]),
              fungicide_application_1 = Herm_17_dat$fungicide_application_1,
              fungicide_application_2 = Herm_17_dat$fungicide_application_2,
              total_fungicide = Herm_17_dat$spray_n,
              harvest_date = as.Date("2017-06-26", format = "%Y-%m-%d"),
              final_assessment = as.Date("2017-05-11", format = "%Y-%m-%d"),
              PM_final_severity = Herm_17_dat$`I_11/05/2017`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`)
               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              )

Herm_17_dat <- cbind(Herm_17_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Herm_17_dat$first_sign_disease[1]-7)-
                                                     Herm_17_dat$planting_date[1],
                                                  39,48,57,64,70,79,87)
                                        )
                          )

@@

Herm_17_m <- Herm_17_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )
sd(Herm_17_dat$PM_final_severity)

# For some weird reason standard deviations are comming back NA in the code above
Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Herm_17_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

@@

Well_18_m <- Well_18_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

@@

#### Define treatment data
```{r Well_18_treatmentDefine}
Herm_19_dat <- PM_MB_19 %>%
   mutate(fungicide_application_1 = 
             case_when(`T/ment.NUM` == 1 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 2 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 3 ~ as.Date("2018-04-23", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 4 ~ as.Date(NA),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(`T/ment.NUM` == 2 ~ as.Date("2018-04-29", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(`T/ment.NUM` == 3 ~ 2,
                       `T/ment.NUM` <= 2 ~ 1,
                       TRUE ~ NA_real_))%>%
   mutate(trial_ref = 
             case_when(TOS.NUM == 1 ~ "mung1819/01",
                       TOS.NUM == 2 ~ "mung1819/02",
                       TRUE ~ NA_character_))%>%
   mutate(planting_date = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-02-04", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-02-18", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(emergence_date = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-02-11", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-02-25", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(final_assessment = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-04-24", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-05-01", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(PM_final_severity = 
             case_when(is.na(`1-5-19.Incedence`) ~ `23-4-19.Incedence`,
                       TRUE ~ `1-5-19.Incedence`))%>%
   mutate(trade_name = 
             case_when(`T/ment.NUM` == 4 ~ NA_character_,
                       TRUE ~ "Folicur"))%>%
   mutate(fungicide_ai = 
             case_when(`T/ment.NUM` == 4 ~ NA_character_,
                       TRUE ~ "tebuconazole"))%>%

@@

Herm_19_dat <- 
   data.frame(trial_ref = Herm_19_dat$trial_ref,
              year = "2019",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = Herm_19_dat$Plot.Lengths,
              plot_width = 2,
              plant_density = NA_character_,
              row_spacing = 0.25,
              replicate = Herm_19_dat$Rep.Num,
              planting_date = Herm_19_dat$planting_date,
              emergence_date = Herm_19_dat$emergence_date,
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2018-04-12", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_19_dat$trade_name),
              fungicide_ai = Herm_19_dat$fungicide_ai,
              dose_ai.ha = Herm_19_dat$dose_ai.ha,
              n_treatment = Herm_19_dat$`T/ment.NUM`,
              fungicide_application_1 = Herm_19_dat$fungicide_application_1,
              fungicide_application_2 = Herm_19_dat$fungicide_application_2,
              total_fungicide = Herm_19_dat$spray_n,
              harvest_date = as.Date("2018-05-22", format = "%Y-%m-%d"),
              final_assessment = Herm_19_dat$final_assessment,
              PM_final_severity = Herm_19_dat$PM_final_severity,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
              meanSq = Herm_19_dat$meanSq
              )

Herm_19_dat$plant_density

unique(Herm_19_dat$plot_length)
mean(Herm_19_dat$plant_density, na.rm = TRUE)

@@

Herm_19_m <- Herm_19_dat %>%
   group_by(trial_ref, n_treatment) %>%
   summarise(year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = NA_character_,
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = unique(meanSq)
   )

# For some weird reason standard deviations are comming back NA in the code above
# Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
#    Herm_17_dat %>%
#    group_by(n_treatment, row_spacing, fungicide_ai) %>%
#    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
#              yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
#    select(c("disease_error","yield_error"))
#

write.csv(
   Herm_17_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage_19_mean.csv",
   row.names = FALSE
)

```{r}
PM19_means <- PM_MB_19 %>%
   group_by(TOS.NUM, `T/ment.NUM`) %>%
   summarise(
      Incidence190423 = mean(`23-4-19.Incedence`, na.rm = TRUE),
      Inc.sd.190423 = sd(`23-4-19.Incedence`, na.rm = TRUE),
      Inc.error.190423 = "Stdev",
      Incidence190501 = mean(`1-5-19.Incedence`, na.rm = TRUE),
      Inc.sd.190501 = sd(`1-5-19.Incedence`, na.rm = TRUE),
      Inc.error.190501 = "Stdev",
      Plot_length = mean(Plot.Lengths, na.rm = TRUE),
      Yield = mean(Yeild/1000, na.rm = TRUE),
      Yield_error = sd(Yeild/1000, na.rm = TRUE),
      AUDPC = mean(AUDPC, na.rm = TRUE),
      meanSq = anova(lm(Yeild/1000 ~ factor(TOS.NUM) + factor(`T/ment.NUM`), data = PM_MB_19))[2,3]
   )

colnames(PM_MB_19)

audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 , c(5, 7, 9)], c(70, 78, 86))

PM_MB_19$AUDPC <- NA
PM_MB_19[PM_MB_19$TOS.NUM == 1 , "AUDPC"] <-
   audpc(PM_MB_19[PM_MB_19$TOS.NUM == 1 , c(5, 7)], c(70, 78))
PM_MB_19[PM_MB_19$TOS.NUM == 2 , "AUDPC"] <-
   audpc(PM_MB_19[PM_MB_19$TOS.NUM == 2 , c(5, 7, 9)], c(70, 78, 86))

boxplot(AUDPC ~ as.factor(`T/ment.NUM`) * as.factor(TOS.NUM) , data = PM_MB_19)

as.Date("2019-05-22") - as.Date("2019-02-04")
as.Date("2019-04-15") - as.Date("2019-02-04")
as.Date("2019-04-23") - as.Date("2019-02-04")
as.Date("2019-05-01") - as.Date("2019-02-04")

>>>>

source("../R/import_data.R")
PM_MB_means <- import_data()

@@

Herm_17_dat <- 
   data.frame(trial_ref = "mung1617/01",
              year = "2017",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = Herm_17_dat$Plot.Length,
              plot_width = 2,
              plant_density = NA,
              row_spacing = Herm_17_dat$`Row.Spacing.(m)`,
              replicate = Herm_17_dat$Rep,
              planting_date = as.Date("2017-02-13", format = "%Y-%m-%d"),
              emergence_date = as.Date("2017-02-20", format = "%Y-%m-%d"),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2017-03-24", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_17_dat$trade_name),
              fungicide_ai = Herm_17_dat$fungicide_ai,
              dose_ai.ha = Herm_17_dat$dose_ai.ha,
              n_treatment = as.numeric(unlist(strsplit(Herm_17_dat$Manage.Trt, "T"))[unlist(strsplit(Herm_17_dat$Manage.Trt, "T")) != ""]),
              fungicide_application_1 = Herm_17_dat$fungicide_application_1,
              fungicide_application_2 = Herm_17_dat$fungicide_application_2,
              total_fungicide = Herm_17_dat$spray_n,
              harvest_date = as.Date("2017-06-26", format = "%Y-%m-%d"),
              final_assessment = as.Date("2017-05-11", format = "%Y-%m-%d"),
              PM_final_severity = Herm_17_dat$`I_11/05/2017`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_17_dat$`Yield.T/Ha`)
               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              )

Herm_17_dat <- cbind(Herm_17_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Herm_17[,c("2017-03-24","I_2/04/2017", "I_11/04/2017", "I_18/04/2017", "I_24/04/2017","I_3/05/2017","I_11/05/2017")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Herm_17_dat$first_sign_disease[1]-7)-
                                                     Herm_17_dat$planting_date[1],
                                                  39,48,57,64,70,79,87)
                                        )
                          )
Herm_17_m
```

@@

Herm_17_m <- Herm_17_dat %>%
   group_by(n_treatment, fungicide_ai,row_spacing) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Herm_17_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

# For some weird reason standard deviations are comming back NA in the code above
Herm_17_m[,c("n_treatment","fungicide_ai","row_spacing", "disease_error","yield_error")] <-
   Herm_17_dat %>%
   group_by(n_treatment, fungicide_ai,row_spacing) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("n_treatment","fungicide_ai","row_spacing","disease_error","yield_error"))

Herm_17_m[Herm_17_m$n_treatment == 1, "fungicide_ai"] <- as.factor("control")
Herm_17_m[Herm_17_m$n_treatment == 1,"dose_ai.ha"] <- NA_real_
Herm_17_m[Herm_17_m$n_treatment == 1, "trade_name"] <- NA

@@

Well_18_m <- Well_18_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             Y_Msquare = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

@@

#### Define treatment data
```{r Well_18_treatmentDefine}
Herm_19_dat <- PM_MB_19 %>%
   mutate(fungicide_application_1 = 
             case_when(`T/ment.NUM` == 1 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 2 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 3 ~ as.Date("2018-04-23", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 4 ~ as.Date(NA),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(`T/ment.NUM` == 2 ~ as.Date("2018-04-29", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(`T/ment.NUM` == 2 ~ 2,
                       `T/ment.NUM` == 1 ~ 1,
                       `T/ment.NUM` == 3 ~ 1,
                       TRUE ~ 0))%>%
   mutate(trial_ref = 
             case_when(TOS.NUM == 1 ~ "mung1819/01",
                       TOS.NUM == 2 ~ "mung1819/02",
                       TRUE ~ NA_character_))%>%
   mutate(planting_date = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-02-04", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-02-18", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(emergence_date = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-02-11", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-02-25", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(final_assessment = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-04-24", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-05-01", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(PM_final_severity = 
             case_when(is.na(`1-5-19.Incedence`) ~ `23-4-19.Incedence`,
                       TRUE ~ `1-5-19.Incedence`))%>%
   mutate(trade_name = 
             case_when(`T/ment.NUM` == 4 ~ NA_character_,
                       TRUE ~ "Folicur"))%>%
   mutate(fungicide_ai = 
             case_when(`T/ment.NUM` == 4 ~ NA_character_,
                       TRUE ~ "tebuconazole"))%>%

@@

#### Input trial data
```{r Herm_19_Trialdat}

Herm_19_dat <- 
   data.frame(trial_ref = Herm_19_dat$trial_ref,
              year = "2019",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = Herm_19_dat$Plot.Lengths,
              plot_width = 2,
              plant_density = NA_character_,
              row_spacing = 0.25,
              replicate = Herm_19_dat$Rep.Num,
              planting_date = Herm_19_dat$planting_date,
              emergence_date = Herm_19_dat$emergence_date,
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2018-04-12", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_19_dat$trade_name),
              fungicide_ai = Herm_19_dat$fungicide_ai,
              dose_ai.ha = Herm_19_dat$dose_ai.ha,
              n_treatment = Herm_19_dat$`T/ment.NUM`,
              fungicide_application_1 = Herm_19_dat$fungicide_application_1,
              fungicide_application_2 = Herm_19_dat$fungicide_application_2,
              total_fungicide = Herm_19_dat$spray_n,
              harvest_date = as.Date("2018-05-22", format = "%Y-%m-%d"),
              final_assessment = Herm_19_dat$final_assessment,
              PM_final_severity = Herm_19_dat$PM_final_severity,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
              meanSq = Herm_19_dat$meanSq,
              AUDPC = Herm_19_dat$AUDPC
              )

Herm_19_m
```

Herm_19_m <- Herm_19_dat %>%
   group_by(trial_ref, n_treatment) %>%
   summarise(year = unique(year),
             location = unique(location),
             host_genotype = "Jade",
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = "40k",
             row_spacing = unique(row_spacing),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             fungicide_ai = unique(fungicide_ai),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             Y_Msquare = unique(meanSq)
   )

# For some weird reason standard deviations are comming back NA in the code above
Herm_19_m[,c("trial_ref","disease_error","yield_error")] <-
   Herm_19_dat %>%
   group_by(trial_ref, n_treatment) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

write.csv(
   Herm_19_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage_19_mean.csv",
   row.names = FALSE
)

@@
